Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-07 doc/manuscript/manuscript.Rmd
removed embarrassing printing and attempt to fix table 2
fix silly mistake

first_axis <- dapc_region$var.contr[, 1]
q95 <- quantile(first_axis, 0.95)
poptab <- dat11 %>% 
  genind2genpop(quiet = TRUE) %>% 
  tab()
near_private <- apply(poptab, 2, function(i) names(i)[which((i/sum(i)) > 0.75)])
near_private <- unlist(near_private[lengths(near_private) == 1])
near_private <- near_private[near_private == "Mexico"]
fa_alleles   <- poptab[, first_axis > q95]
mx_percent   <- t(fa_alleles[, names(near_private)])/colSums(fa_alleles)
mx_percent   <- prettify(mx_percent[, "Mexico", drop = TRUE], TRUE)
mx_loci      <- substr(names(mx_percent), 1, 3)
mx_alleles   <- substr(names(mx_percent), 8, 11)
mx_allele_string <- glue::glue("alleles {mx_alleles[1]}, {mx_alleles[2]}, and {mx_alleles[3]} in loci {mx_loci[1]}, {mx_loci[2]}, and {mx_loci[3]}")

@@

WAnova  <- lm(Severity ~ Field + Year, data = WA, contrasts = "contr.helmert")
WAnova  <- anova(WAnova)
PWA     <- signif(WAnova[1, 5], 3)
PWA
```

>>>>

first_axis <- dapc_region$var.contr[, 1]
q95 <- quantile(first_axis, 0.95)
poptab <- dat11 %>% 
  genind2genpop(quiet = TRUE) %>% 
  tab()
near_private <- apply(poptab, 2, function(i) names(i)[which((i/sum(i)) > 0.75)])
near_private <- unlist(near_private[lengths(near_private) == 1])
near_private <- near_private[near_private == "Mexico"]
fa_alleles   <- poptab[, first_axis > q95]
mx_percent   <- t(fa_alleles[, names(near_private)])/colSums(fa_alleles)[names(near_private)]
mx_percent   <- prettify(mx_percent[, "Mexico", drop = TRUE], TRUE)
mx_loci      <- substr(names(mx_percent), 1, 3)
mx_alleles   <- substr(names(mx_percent), 8, 11)
mx_allele_string <- glue::glue("alleles {mx_alleles[1]}, {mx_alleles[2]}, and {mx_alleles[3]} in loci {mx_loci[1]}, {mx_loci[2]}, and {mx_loci[3]}")

@@

WAnova  <- lm(Severity ~ Field + Year, data = WA, contrasts = "contr.helmert")
WAnova  <- anova(WAnova)
PWA     <- signif(WAnova[1, 5], 3)
```
